%-------------------------
% Resume in Latex
% Author : Sam Jordan
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\textbf{\small#3}} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Samuel Musgrave Jordan} \\ \vspace{1pt}
    \small +44 7470326602 $|$ \href{mailto:samuelmjordan@outlook.com}{\underline{samuelmjordan@outlook.com}} $|$
    \href{https://www.linkedin.com/in/samuel-musgrave-jordan}{\underline{linkedin.com/in/samuel-musgrave-jordan/}} $|$
    \href{https://github.com/jordan12sam}{\underline{github.com/jordan12sam}}
\end{center}

%----------Summary------------------
Backend software engineer with 3 years of experience architecting and delivering high-performance Java applications in the fintech sector. Based in London, UK.


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

\resumeSubheading
  {Engine by Starling}{London, UK}
  {Software Engineer {\normalfont $|$ Java, Guice, Postgres, TeamCity, Kubernetes, AWS}}{August 2024 -- Present}
  \resumeItemListStart
    \resumeItem{Backend developer for a greenfield lending service, delivering a comprehensive platform that interfaces with mobile apps, web management portals, and via API. Implemented core business logic and integration points using Java and Guice.}
    \resumeItem{Architected a highly configurable lending system using domain-driven design principles, enabling clients to customize application workflows, credit decisioning rules, and market-specific requirements through configuration rather than code changes.}
    \resumeItem{Successfully delivered the platform to production within an aggressive 9-month timeline, utilizing AWS infrastructure and Kubernetes for scalable deployment while maintaining high availability and performance standards.}
  \resumeItemListEnd

\resumeSubheading
  {American Express}{Brighton/London, UK}
  {Software Engineer {\normalfont $|$ Java, Spring, Postgres, Jenkins}}{September 2022 -- August 2024}
  \resumeItemListStart
    \resumeItem{Contributed to American Express's global statements platform, processing over 10 million daily statement documents with a near zero failure rate. Implemented critical features using Java Spring, ensuring scalability and maintaining strict financial compliance standards.}
    \resumeItem{Spearheaded the development of an innovative bank statement generation service, resulting in annual cost savings exceeding £1M anually. Designed and implemented a fault-tolerant microservice architecture utilizing Kafka for event streaming, Postgres for persistent storage, and Redis for caching.}
    \resumeItem{Established robust quality assurance practices by implementing comprehensive JUnit test suites. Automated deployment pipelines using Jenkins, enabling continuous integration and deployment.}
  \resumeItemListEnd

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/jordan12sam/Raytracer}{Raytracer}} $|$ \emph{C++, CMake, GLSL, OpenGL}}{}
          \resumeItemListStart
            \resumeItem{Implemented a ray tracer in C++, utilizing OpenGL for graphics rendering.}
            \resumeItem{Features reflections aswell as ambient, specular and diffuse lighting effects to create realistic and visually appealing 3D images.}
            \resumeItem{Chose an object-oriented design to allow for easy modification and expansion.}
            \resumeItem{Utilized efficient algorithms and data structures to optimize performance and achieve real-time rendering.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{\href{https://github.com/jordan12sam/Orderbook}{Orderbook}} $|$ \emph{C++, CMake, Gtest}}{}
          \resumeItemListStart
            \resumeItem{Developed a limit order book in C++.}
            \resumeItem{Can place/cancel limit orders. Orders are matched with a standard price-time priority.}
            \resumeItem{Utilized the correct data structures to optimise performance, including min/max heaps for bid/ask books and doubly linked lists for limit levels. Hashmaps of orders and limit levels are maintained to reduce look-up complexity.}
            \resumeItem{Built with unit tests in the gtest library and automated via github actions.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++, SQL} \\
     \textbf{Frameworks \& Libraries}{: Spring, Guice} \\
     \textbf{Developer Tools}{: Redis, Couchbase, Postgres, Kafka, Maven, Gradle, Jenkins, TeamCity, Kubernetes, AWS} \\
    }}
 \end{itemize}

 %-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Southampton}{Southampton, UK}
      {\normalfont{\textit{MEng Aerospace \& Astronautics, Upper Second Class Honours}}}{Sep. 2018 -- Jun. 2022}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
