%-------------------------
% Resume in Latex
% Author : Sam Jordan
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
    \item\small{
            {#1 \vspace{-2pt}}
    }
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\textbf{\small#3}} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
\textbf{\Huge \scshape Samuel Musgrave Jordan} \\ \vspace{1pt}
\small +44 7470326602 $|$ \href{mailto:samuelmjordan@outlook.com}{\underline{samuelmjordan@outlook.com}} \\ \vspace{4pt}
\href{https://www.linkedin.com/in/samuel-musgrave-jordan}{\underline{linkedin}} $|$
\href{https://github.com/samuelmjordan}{\underline{github}} $|$
\href{https://samuelmjordan.dev}{\underline{samuelmjordan.dev}}
\end{center}

%----------Summary------------------
Backend software engineer with 3 years of experience architecting and delivering high-performance Java applications in the fintech sector. Based in London, UK. Eligible for H1B sponsorship.

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Engine by Starling}{London, UK}
{Software Engineer {\normalfont $|$ Java, Guice, Postgres, TeamCity, Kubernetes, AWS}}{August 2024 -- Present}
\resumeItemListStart
\resumeItem{Backend developer for Engine, a bank-in-a-box SaaS product operating as core infrastructure for banks worldwide.}
\resumeItem{Built greenfield lending origination service from scratch, implementing API endpoints, business logic, and payment processing using Java and Guice.}
\resumeItem{Designed highly configurable system enabling banks to customize credit rules, application workflows, and compliance requirements through configuration rather than code changes.}
\resumeItem{Delivered platform to production within aggressive 9-month timeline, deployed on AWS with Kubernetes orchestration.}
\resumeItem{Led a small cross-functional subteam developing web management portal, coordinating backend services with frontend integration. Coordinated with product managers and clients directly.}
\resumeItemListEnd

\resumeSubheading
{American Express}{Brighton/London, UK}
{Software Engineer {\normalfont $|$ Java, Spring, Postgres, Jenkins}}{September 2022 -- August 2024}
\resumeItemListStart
\resumeItem{Contributed to global statements platform processing 10M+ daily documents with near-zero failure rate using Java Spring.}
\resumeItem{Built a platform to handle bank statement generation in-house, saving £1M+ annually. Implemented microservice architecture with Kafka, Postgres, and Redis.}
\resumeItem{Automated deployment pipelines using Jenkins and established comprehensive JUnit test coverage.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{\href{https://axolhost.com}{Game Server Hosting Platform}} $|$ \normalfont{Java, Spring, Next.js, TypeScript, Postgres}}{}
\resumeItemListStart
\resumeItem{Built Minecraft server hosting platform with Stripe billing and authentication integration.}
\resumeItem{Implemented cloud server provisioning, DNS management, and game process spawning via async job queues.}
\resumeItem{Deployed live platform serving real customers with automated resource management.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{\href{https://github.com/samuelmjordan/media-server}{Personal Media Server}} $|$ \normalfont{OCaml, Dream, Postgres, HTMX}}{}
\resumeItemListStart
\resumeItem{Developed streaming platform with automatic library scanning and TMDB metadata integration.}
\resumeItem{Implemented HLS protocol requests for seamless video playback and seeking in browsers and VLC.}
\resumeItem{Utilised FFMPEG for live video transcoding.}
\resumeItem{Built using functional programming principles with OCaml and modern web technologies.}
\resumeItemListEnd
\resumeProjectHeading
{\textbf{\href{https://github.com/samuelmjordan/raytracer}{GPU Raytracer}} $|$ \normalfont{C++, OpenGL, GLSL}}{}
\resumeItemListStart
\resumeItem{Implemented GPU-accelerated raytracer with physically-based lighting and recursive reflections.}
\resumeItem{Renders complex 3D scenes entirely in fragment shaders for real-time performance.}
\resumeItem{Optimized rendering pipeline using efficient algorithms and OpenGL best practices.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\textbf{Languages}{: Java, Python, C/C++, OCaml, TypeScript, SQL} \\
\textbf{Frameworks \& Libraries}{: Spring, Guice, Next.js, Dream} \\
\textbf{Developer Tools}{: Redis, Postgres, Kafka, Maven, Gradle, Jenkins, TeamCity, Kubernetes, AWS, Stripe} \\
}}
\end{itemize}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of Southampton}{Southampton, UK}
{\normalfont{\textit{MEng Aerospace \& Astronautics, Upper Second Class Honours}}}{Sep. 2018 -- Jun. 2022}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}